
```markdown
---
title: "Data Cleaning and Exploration Report"
author: "Your Name"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This report aims to document the data cleaning and exploration process for the given dataset. We will use R to perform various tasks such as handling missing values, visualizing data distributions, and making data quality improvements.

## Load Libraries and Data

```{r load-libraries-and-data}
# Install and load required libraries
install.packages("dplyr")
library(dplyr)

install.packages("ggplot2")
library(ggplot2)

# Read data from CSV file
data <- read.csv("data/finalTrain.csv")
```

## Initial Data Inspection

```{r initial-data-inspection}
# Check first few rows of the data
head(data, 3)

# Check rows with missing values in "Delivery_person_Age"
head(data[is.na(data$Delivery_person_Age), ], 3)

# Check the data types and number of non-null values for each column
summary(data)
```

## Data Cleaning

```{r data-cleaning}
# Drop columns with no information or unique values
data <- data %>% select(-Delivery_person_ID, -ID, -Time_Orderd, -Time_Order_picked)

# Check the data types and number of non-null values for each column after dropping columns
summary(data)

# Check first few rows of the data after dropping columns
head(data, 3)
```

## Exploratory Data Analysis

### Distribution of Delivery Person Age

```{r eda-age-distribution}
# Plot histogram with density curve for "Delivery_person_Age"
histplotcount_func("Delivery_person_Age", data, 5)
```

### Handling Missing Values

```{r handle-missing-values}
# Calculate the mean of "Delivery_person_Age" to fill missing values
mean_age <- mean(data$Delivery_person_Age)

# Fill missing values in "Delivery_person_Age" with the mean
data$Delivery_person_Age <- replace(data$Delivery_person_Age, is.na(data$Delivery_person_Age), mean_age)
```

### Distribution of Delivery Person Ratings

```{r eda-ratings-distribution}
# Remove rows where "Delivery_person_Ratings" is 6
data <- data %>% filter(Delivery_person_Ratings != 6)

# Plot histogram with density curve for "Delivery_person_Ratings"
histplotcount_func("Delivery_person_Ratings", data, 5)
```

# Conclusion

This report has provided an overview of the data cleaning and exploration steps performed on the given dataset. Additional analyses and visualizations can be added based on specific requirements.

```

